\documentclass[11pt,a4paper]{article}

% ==================== PACKAGES ====================
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{siunitx}

% ==================== PAGE SETUP ====================
\geometry{
    a4paper,
    left=2.5cm,
    right=2.5cm,
    top=2.5cm,
    bottom=2.5cm
}

% ==================== HYPERLINKS ====================
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan,
    citecolor=blue,
    pdftitle={Power Electronics I - Course Project},
    pdfauthor={Azab, Saber, Abdelhafez}
}

% ==================== GRAPHICS PATH ====================
\graphicspath{{figures/}}

% ==================== DOCUMENT INFO ====================
\title{
    \textbf{Power Electronics I} \\
    \Large{Course Project Report} \\
    \large{Controlled Rectifiers for Battery Charging}
}

\author{
    Mohammed Azab \and Basant Saber \and Habiba Abdelhafez \\
    \\
    German University in Cairo (GUC) \\
    Faculty of Engineering \\
    \\
    \textbf{Instructor:} Dr.-Ing. Moustafa Adly
}

\date{Fall Semester 2025 \\ November 25, 2025}

% ==================== DOCUMENT BEGIN ====================
\begin{document}

% Title Page
\maketitle
\newpage

% Table of Contents
\tableofcontents
\newpage

% ==================== ABSTRACT ====================
\section*{Abstract}
\addcontentsline{toc}{section}{Abstract}

This project presents the design and analysis of controlled rectifier circuits using thyristors (SCRs) for battery charging applications. Three different rectifier configurations are implemented and simulated in MATLAB: half-wave controlled rectifier, full-wave center-tapped rectifier, and full-wave bridge rectifier. The study examines the relationship between firing angle and charging characteristics, including average and RMS voltage and current values. Performance comparisons demonstrate that full-wave configurations provide superior charging performance with reduced charging times and improved efficiency compared to half-wave rectifiers. The analysis includes circuit modeling, waveform generation, and comprehensive performance metrics for each topology.

\newpage

% ==================== MAIN CONTENT ====================

% ==================== PART I ====================
\input{chapters/part1_introduction}
\input{chapters/part1_design}
\input{chapters/part1_results}
\input{chapters/part1_discussion}

\newpage

% ==================== PART II ====================
\input{chapters/part2_introduction}
\input{chapters/part2_discussion}

\newpage

% ==================== CONCLUSION ====================
\input{chapters/conclusion}

\newpage

% ==================== APPENDIX ====================
\appendix

\section{MATLAB Code Overview}

The battery charger analysis was implemented using three main MATLAB functions:

\subsection{System Parameters (params.m)}
Defines all system parameters: supply voltage (230V RMS, 50Hz), battery specifications (20V, 0.1$\Omega$, 50Ah), initial state of charge (12\%), thyristor parameters (forward drop 1.5V), and firing angle ranges.

\subsection{Half-Wave Rectifier (half\_wave\_charger.m)}
Implements single-phase half-wave controlled rectifier with one thyristor. Calculates average output voltage $V_{dc} = \frac{V_m}{2\pi}(1+\cos\alpha) - V_t$, charging current, SoC progression, and power losses. Generates comprehensive waveform plots and performance analysis.

\subsection{Full-Wave Center-Tapped (full\_wave\_ct\_charger.m)}
Analyzes full-wave rectifier with center-tapped transformer and two thyristors. Provides double the output frequency and improved performance: $V_{dc} = \frac{2V_m}{\pi}(1+\cos\alpha) - V_t$. Includes comparative analysis with half-wave configuration.

\subsection{Full-Wave Bridge (full\_wave\_bridge\_charger.m)}
Implements bridge configuration with four thyristors. Uses standard transformer (no center-tap required). Accounts for two thyristor drops: $V_{dc} = \frac{2V_m}{\pi}(1+\cos\alpha) - 2V_t$. Electrically equivalent to center-tapped but mechanically simpler.

All functions feature flexible input parsing, comprehensive plotting with LaTeX formatting, automatic figure saving, and detailed performance metrics output.

\end{document}
